A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-02-08 revisionNotel2_responses.tex
grammerly checked

\subsection*{Revision notes: rebuttal}  
%Where the authors disagree with a reviewer, they must provide a clear response by a rebuttal if some of the reviewer’s comments cannot be revised. 
%動之以情，和氣誠懇地說明原委 https://www.mdpi.com/journal/cancers/instructions#editorial_procedure
% *** Alex: yes, please answer the reviewer politely 和氣誠懇地 and tell him that 
%in a respectful and considerate manner.
We appreciate the reviewer for the critical comment and apology for short of experiment results. 
%We modified "Material and Methods",  Results and Discussion of manuscript according the new evidence.
It is encouraged for multidisciplinary studies that use complementary computational and  experimental approaches to address challenging cancer research.
%下一篇文章的內容。目前在計畫中，但還沒有開始進行
These in vitro and in vivo validation experiments will be undertaken in Alex's laboratory (one of our co-authors).
We plan to analysis on mRNA (e.x. qRT-PCR) and protein (e.x. western blot) of HNSCC cell lysate to confirm expression of those candidate genes.
%mRNA expression level in HNSCC cell lines (其他文章已有發表 overexpression）
The effect of over-expression and knockdown of gene by lenti-viral clones should be observed on cell function assay (e.x. proliferation, migration, and invasion) and mouse xenograft model (e.x. tumor growth). %這些都需要一年以上的時間
%their rationale for looking into TMSB4X is not strongly supported by the available data.

% 其實文章真正的目標是  bioinformatics workflow，而不是 discovered biomarkers itself (see TCGA marker paper\cite{Lawrence2015a})
Moreover, this bioinformatics paper is providing targets and supporting community's rationale for looking into these HNSCC candidates by in vitro and in vivo validation. %Collectively, these findings provide new insights into HNSCC and suggest that shared and unique alterations might be leveraged to accelerate progress in prevention and therapy across tumour types\cite{Lawrence2015a}.
%We open invitation for research community by potential support their rationale for looking into these HNSCC candidates.
%邀請科學家們一塊兒來繼續研究下去找出幫助癌症患者的方法
%the rest of the analysis seems fine, but 
%文章的初衷、跨領域：如同deep leaning Keras API，推廣研究者一個有效的方法 
We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on TCGA or their in-house HNSCC dataset. % to find more useful biomarkers. % or even other cancer types
% to allow successful repetition and extension of analyses based on original data
A good practice of research reproducibility is necessary in order to allow %previously developed methodology to be effectively applied on new data, or to allow 
reuse of code and results for new projects. %In other words, good habits of reproducibility
It may actually turn out to be a time-saver in the longer run.
When a result can be reproduced by multiple scientists, it will also validate our original results and readiness to progress to the next phase of research. 
%why reproducibility?
%Reproducible Bioinformatics Project provides a general schema and an infrastructure to distribute robust and reproducible workflows. Thus, it guarantees to final users the ability to repeat consistently any analysis independently by the used UNIX-like architecture.
%Utility of this model would facilitate development of more individualized therapy for HNSCC patients and improve prognosis.

Once those candidates are identified by Alex's laboratory (or community) as the targets, the compound screening could facilitate development of more individualized therapy for HNSCC patients and improve prognosis. %help to discover a potential drug for HNSCC therapy.
%https://www.mdpi.com/journal/cancers/instructions

>>>>

\subsection*{Revision notes: rebuttal}  
%Where the authors disagree with a reviewer, they must provide a clear response by a rebuttal if some of the reviewer’s comments cannot be revised. 
%動之以情，和氣誠懇地說明原委 https://www.mdpi.com/journal/cancers/instructions#editorial_procedure
% *** Alex: yes, please answer the reviewer politely 和氣誠懇地 and tell him that 
%in a respectful and considerate manner.
We appreciate the reviewer for the critical comment and apology for short of experiment results. 
%We modified "Material and Methods",  Results and Discussion of manuscript according the new evidence.
It is encouraged for multidisciplinary studies that use complementary computational and experimental approaches to address challenging cancer research.
%下一篇文章的內容。目前在計畫中，但還沒有開始進行
These in vitro and in vivo validation experiments will be undertaken in Alex's laboratory (one of our co-authors).
We plan to analyze mRNA (e.x. qRT-PCR) and protein (e.x. western blot) of HNSCC cell lysate to confirm the candidate genes' expression.
%mRNA expression level in HNSCC cell lines (其他文章已有發表 overexpression）
The effect of over-expression and knockdown of the gene by lentiviral clones should be observed on cell function assay (e.x. proliferation, migration, and invasion) and mouse xenograft model (e.x. tumor growth). %這些都需要一年以上的時間
%their rationale for looking into TMSB4X is not strongly supported by the available data.

% 其實文章真正的目標是  bioinformatics workflow，而不是 discovered biomarkers itself (see TCGA marker paper\cite{Lawrence2015a})
Moreover, this bioinformatics paper provides targets and supports the community's rationale for looking into these HNSCC candidates by in vitro and in vivo validation. %Collectively, these findings provide new insights into HNSCC and suggest that shared and unique alterations might be leveraged to accelerate progress in prevention and therapy across tumour types\cite{Lawrence2015a}.
%We open invitation for research community by potential support their rationale for looking into these HNSCC candidates.
%邀請科學家們一塊兒來繼續研究下去找出幫助癌症患者的方法
%the rest of the analysis seems fine, but 
%文章的初衷、跨領域：如同deep leaning Keras API，推廣研究者一個有效的方法 
We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on TCGA or their in-house HNSCC dataset. % to find more useful biomarkers. % or even other cancer types
% to allow successful repetition and extension of analyses based on original data
A good practice of research reproducibility is necessary to allow the reuse of code and results for new projects.
%previously developed methodology to be effectively applied on new data, or to allow 
%reuse of code and results for new projects. %In other words, good habits of reproducibility
It may turn out to be a time-saver in the longer run.
When multiple scientists can reproduce a result, it will also validate our initial results and readiness to progress to the next research phase. 
%why reproducibility?
%Reproducible Bioinformatics Project provides a general schema and an infrastructure to distribute robust and reproducible workflows. Thus, it guarantees to final users the ability to repeat consistently any analysis independently by the used UNIX-like architecture.
%Utility of this model would facilitate development of more individualized therapy for HNSCC patients and improve prognosis.

Once Alex's laboratory and the community identify those candidates as the targets, the compound screening could facilitate more individualized therapy for HNSCC patients and improve prognosis. %help to discover a potential drug for HNSCC therapy.
%https://www.mdpi.com/journal/cancers/instructions
